\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changes to captions

\begin{figure}[!hbt]
    \centering
    \small
    \includegraphics[width = \textwidth, height=14cm]{Figs/lossboxplots_1.pdf}
    \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$. A value less than 1 indicates that the coherent forecasts improvement upon base forecasts.  Although it is not clearly apparent in the plot, for OLS there are some values in the Spend-WSE that are slightly greater than 1.}\label{fig:BaseVSRecon_Fc}
\end{figure}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		\hline
		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
		\hline
		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\ 
		Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\ 
		Spend WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\ 
		\hline
	\end{tabular}

	\caption{Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
	\label{tab:lossVmethods} 
\end{table}

>>>>

\begin{figure}[!hbt]
    \centering
    \small
    \includegraphics[width = \textwidth, height=14cm]{Figs/lossboxplots_1.pdf}
    \caption{{\color{blue} Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}}\label{fig:BaseVSRecon_Fc}
\end{figure}

@@

\begin{table}[ht]
	\centering
{\color{blue}	
	\begin{tabular}{lrrrrrr}
		\hline
		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
		\hline
		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\ 
		Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\ 
		Spend WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\ 
		\hline
    \end{tabular}
}
	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.  The lowest mean is always provided by MinT, for structural-WSE, the average loss for MinT is significantly than every other method.}}
	\label{tab:lossVmethods} 
\end{table}
